---
title: "P8105 Homework3"
output: github_document
---

```{r setup}
library(tidyverse)
library(p8105.datasets)
data("instacart")
```

## Problem 1
- How many aisles are there, and which aisles are the most items ordered from?

```{r}
instacart %>% 
  group_by(aisle_id, aisle) %>% 
  count(aisle_id, aisle, name = "n_obs") %>% 
  arrange(desc(n_obs))

```
There are 134 aisles, and the most items ordered from fresh vegetables.

- Make a plot that shows the number of items ordered in each aisle, limiting this to aisles with more than 10000 items ordered. Arrange aisles sensibly, and organize your plot so others can read it.



```{r}
instacart %>% 
  group_by(aisle_id, aisle) %>% 
  count(aisle_id, aisle, name = "n_obs") %>% 
  filter(n_obs > 10000) %>% 
  arrange(desc(n_obs)) %>% 
  mutate(aisle = forcats::fct_reorder(aisle, n_obs, .desc = TRUE)) %>% 
  ggplot(aes(x = aisle, y = n_obs)) +
  coord_flip()+
  geom_bar(stat = "identity") +
  labs(y = "number of orders",
       x = "aisle")
 
```

- Make a table showing the three most popular items in each of the aisles “baking ingredients”, “dog food care”, and “packaged vegetables fruits”. Include the number of times each item is ordered in your table.

```{r}
instacart %>% 
  janitor::clean_names() %>% 
  filter(aisle %in% c("baking ingredients", "dog food care", "packaged vegetables fruits")) %>% 
  group_by(aisle, product_name) %>% 
  summarize(n = n()) %>% 
  filter(n == max(n)) %>% 
  arrange(desc(n)) %>% 
  rename("aisle name" = aisle, "product name" = product_name, 
         "number of order" = n) %>% 
  knitr::kable()
  
  
 
```


- Make a table showing the mean hour of the day at which Pink Lady Apples and Coffee Ice Cream are ordered on each day of the week; format this table for human readers (i.e. produce a 2 x 7 table).

```{r}
instacart %>% 
  janitor::clean_names() %>% 
  filter(product_name %in% c("Pink Lady Apples", "Coffee Ice Cream")) %>% 
  select(product_name, order_dow, order_hour_of_day) %>% 
  group_by(product_name,order_dow) %>% 
  summarise(avg_hour = round(mean(order_hour_of_day), 2)) %>% 
  spread(key = order_dow, value = avg_hour) %>% 
  rename("product name" = product_name) %>%
  knitr::kable()
```

## Problem 2

- Load, tidy, and otherwise wrangle the data. Your final dataset should include all originally observed variables and values; have useful variable names; include a weekday vs weekend variable; and encode data with reasonable variable classes. Describe the resulting dataset (e.g. what variables exist, how many observations, etc).

```{r}
accel_df <- read_csv("./data/accel_data.csv") %>% 
  janitor::clean_names() %>% 
  pivot_longer(
    activity_1:activity_1440,
    names_to = "activity", 
    names_prefix = "activity_", 
    values_to = "counts"
  ) %>% 
  mutate(weekday = case_when(
    day == "Sunday"  | day == "Saturday" ~ "weekend",
    day_id != "Saturday" | day_id != "Sunday" ~ "weekday",
    TRUE ~ ""
  ))
```
I used pivot longer to transform the dataset from a wide form to a long one, and kept the activity categories and the count of the activity in different columns. Besides, I also create a new variable to distinguish weekend and weekday. In my dataset, there are 6 variables: week, day_id, day, activity, counts, and weekday, and 50400 observations. 

- Traditional analyses of accelerometer data focus on the total activity over the day. Using your tidied dataset, aggregate accross minutes to create a total activity variable for each day, and create a table showing these totals. Are any trends apparent?

```{r}
accel_df %>% 
  group_by(day) %>% 
  summarise(total_activity = sum(counts)) %>% 
  arrange(desc(total_activity))
  
```
After tidying the dataset, we can find that most activities reside in weekdays, particularly when approaching weekend and after Wednesday. We can find the trend that people don't actually do more activities during weekend, Monday, and Tuesday as they do in Thursday, Wednesday, and Friday.

- Accelerometer data allows the inspection activity over the course of the day. Make a single-panel plot that shows the 24-hour activity time courses for each day and use color to indicate day of the week. Describe in words any patterns or conclusions you can make based on this graph.

```{r}
accel_df %>% ggplot(aes(x = day, y = counts, color = week)) +
  geom_point(alpha = .5) +
  viridis::scale_color_viridis(name = "week", 
                               discrete = FALSE)
```
From the scatterplot, we can see the trend that most activities over the course of the day reside in previous weeks. With the weeks increasing, the counts start to decrease. Interestingly, people who do activities on Thursday presume their activity volume even till week 5.

## Problem 3

```{r}
library(p8105.datasets)
data("ny_noaa")
```
- Do some data cleaning. Create separate variables for year, month, and day. Ensure observations for temperature, precipitation, and snowfall are given in reasonable units. For snowfall, what are the most commonly observed values? Why?

```{r}
noaa_df <- ny_noaa %>% 
  janitor::clean_names() %>% 
  separate(date, c("year", "month", "day"), sep = "-") %>% 
  mutate(tmax = as.double(tmax) / 10, 
         tmin = as.double(tmin) / 10, 
         prcp = prcp / 10,
         month = month.name[as.integer(month)], 
         year = as.integer(year))
```

- Make a two-panel plot showing the average max temperature in January and in July in each station across years. Is there any observable / interpretable structure? Any outliers?

```{r}
noaa_df %>% 
  filter(month %in% c("January", "July")) %>% 
  group_by(year, month) %>% 
  summarise(mean_temp = mean(tmax, na.rm = TRUE)) %>% 
  ggplot(aes(x = year, y = mean_temp)) +
  geom_line() +
  facet_grid(.~ month)
#Check the outlier with boxplot.
noaa_df %>% 
  filter(month %in% c("January", "July")) %>% 
  group_by(year, month) %>% 
  summarise(mean_temp = mean(tmax, na.rm = TRUE)) %>% 
  ggplot(aes(x = year, y = mean_temp)) +
  geom_boxplot() +
  facet_grid(.~ month)
```



